Naive Bayes Classifier

### 2019-07-03 NB_v3_new_data_input.Rmd
Update

#Train Model, Predict & Evaluate for Subject
This block predicts whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. 
```{r bayes_training subject}
# Train the classifier on training data, then test on test dataset, and full dataset.
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject, laplace=1)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
comments_all_pred_subject <- predict(comments_classifier_subject, comments_all)
```

>>>>

Here is where I need to add code to format NEW datasets, and drop the text DTM into the trained classifier. Pseudo-code is:
  Import Sp19_comments.csv
  Extract ta.comments to a new data object
  Run the ta.comments object through processing:

{r input data}
#Read in TA comments from NEW CSV file.
base_dataVERB <- read_csv(file='data/coded_full_comments_dataset_Spring18anonVERB.csv')

#Change "structure" element from character to a factor for analysis.
comments_rawVERB$structure <- factor(comments_rawVERB$structure)
str(comments_rawVERB$structure)
table(comments_rawVERB$structure)

#Convert data set to a volative corpus using "tm" library.
{r corpusmaker}
#Create the volatile corpus that contains the "text" vector from data frame.
comments_corpusVERB_R <- VCorpus(VectorSource(comments_rawVERB_R$text))
print(comments_corpusVERB_R)

#Use "as.character" function to see what a single text comment looks like.
as.character(comments_corpusVERB_R[[5]])

{r textcleanup}
#Convert text to all lower case letters.
comments_corpus_cleanVERB_R <- tm_map(comments_corpusVERB_R, content_transformer(tolower))

#Look at an example of cleaned text comment to see if cleaned comment matches what is expected. Change the value inside double brackets to look at a different comment.
as.character((comments_corpus_cleanVERB_R[[5]]))

{r tokenizer}
NLP_Tokenizer <- function(x) {
      unlist(lapply(ngrams(words(x), 1), paste, collapse = " "), use.names = FALSE)
}

comments_dtm_1gram <- DocumentTermMatrix(comments_corpus_cleanVERB_R, control=list(tokenize = NLP_Tokenizer))
comments_dtm_1gram_tidy <- tidy(comments_dtm_1gram)
inspect(comments_dtm_1gram)

Some subset of the above steps SHOULD convert the new dataset to a readable format for comparison. END GOAL is to have a data object that can be plugged into the "predict" command.

***
Break
***
